---
title: "Fourier transform"
output: html_document
editor_options: 
  chunk_output_type: console
---

We can use the source function to run the contents of another R script file.

```{r}
source("setup.R")
```

Now let's bring in the data that I have in the R project repo file: ./data/pse

# PSE experiment data

```{r}
results <- list.files("data/pse")
raw_data <- NULL

for (i in seq_along(results)) {
  temp <- import(paste0("data/pse/", results[i]))
  combined_data <- rbind(raw_data, temp)
}
```

# random cleaning unique to my experiment

```{r}
# add count on file to sum data points later

combined_data <- combined_data %>%
  mutate('count' = rep(1,nrow(combined_data)))

# switch "correct answer" to "right"
left_rightdata <- combined_data
rightdata <- left_rightdata %>%
  filter(Staircase.CorrectAns == 'right')
leftdata <- left_rightdata %>%
  filter(Staircase.CorrectAns == 'left')
rightdata$Staircase.response <- ifelse(rightdata$Staircase.response == 0, 1, 0)
combined_data <- rbind(leftdata, rightdata)

# arrange back to original staircase order
combined_data <- combined_data %>%
  arrange(Staircase.thisRepN)
```

Now we can use dplyr to summarize the data:

```{r}
effects <- combined_data %>%
  group_by(participant, Staircase.SOA) %>%
  summarize(avg_eff = mean(Staircase.intensity))
```

```{r}
# I use this if I want to look at individual subject data but in here we only have one subject so far
subject_no <- 'it_021522'

combined_data %>%
  filter(participant == subject_no) %>%
  group_by(participant, 'Displacement' = Staircase.intensity, Staircase.SOA) %>%
  summarize(PSE = mean(Staircase.response)) %>%
  ggplot(aes(Displacement, PSE, color = as.factor(Staircase.SOA))) +
  geom_point() +
  theme_minimal() +
  ggtitle(subject_no)
```

# Modulation exp data

```{r}
results_mod <- list.files("data/modulation")
raw_data_mod <- NULL

for (i in seq_along(results_mod)) {
  temp <- import(paste0("data/modulation/", results_mod[i]))
  mod_data <- rbind(raw_data_mod, temp)
}
```

Using dplyr to organize my data file - the Select() function to grab the variables I'm interested in and Mutate() to code the character string 'left' and 'right' into binary.

```{r}
fe_mod <- mod_data %>%
  select(participant, PSE, SOA, trials.thisTrialN, trial_resp_2.keys) %>%
  mutate(LR_coded = ifelse(mod_data$trial_resp_2.keys == 'left', 1, 0),
         SOA = mod_data$SOA * 10)

```

More organization with dplyr and then graph it

```{r}
mod_eff <- fe_mod %>%
  #this line of code is useful if you want to filter to look at one subject at a time
  #filter(participant == subject_no) %>%
  group_by(SOA) %>%
  summarize(PSE = mean(LR_coded))

mod_eff %>%
  ggplot(aes(SOA, PSE)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  theme_minimal()
```

# Fourier Transform on Behavioral Data


```{r}
fft_list <- spectrum(mod_eff)
fft_vector <- fft_list[["freq"]]
fft(fft_vector)
```

```{r}
fft_vector <- mod_eff$PSE
fft(fft_vector)
```

